\subsection{Variants of normed groups}
\label{sec:normed_groups2}

This subsection continues some of the theory of (pseudo)-normed groups,
started in Subsection~\ref{sec:normed_groups}.

\begin{definition}
  \label{p-banach}
  \lean{pBanach}
  \leanok
  A $p$-Banach space $V$ is a complete topological $\mathbb R$-vector space
  whose topology is induced by a $p$-norm;
  that is, a norm satisfying $\|rv\| = |r|^p\|v\|$.
\end{definition}

\begin{lemma}
  \label{p-banach-r-normed}
  \uses{p-banach, normed_with_aut}
  \lean{pBanach.choose_normed_with_aut}
  \leanok
   A $p$-Banach $V$ is (up to non-canonical choice) an $r$-Banach $\mathbb Z[T^{\pm 1}]$-module, where $r=2^{-p}$.
   (See Definition~\ref{normed_with_aut} for the definition of $r$-normed $\mathbb Z[T^{\pm 1}]$-modules.)
\end{lemma}

\begin{proof}
  \leanok
  Obvious.
\end{proof}

\begin{definition}
  \label{png-cats}
  \uses{chpng-Tinv}
  \lean{CompHausFiltPseuNormGrp.large_category, CompHausFiltPseuNormGrp₁.category_theory.large_category, ProFiltPseuNormGrp.large_category, ProFiltPseuNormGrp₁.category_theory.large_category, ProFiltPseuNormGrpWithTinv₁.category_theory.large_category}
  \leanok
  We will consider the following categories:
  \begin{itemize}
    \item $\text{CHPNG}$ the category of CH-filtered pseudo-normed groups with bounded morphisms.
    \item $\text{CHPNG}_1$ the category of exhaustive CH-filtered pseudo-normed groups with strict morphisms.
    \item $\text{ProfinPNG}$ the category of profinitely filtered pseudo-normed groups with bounded morphisms.
    \item $\text{ProfinPNG}_1$ the category of exhaustive profinitely filtered pseudo-normed groups with strict morphisms.
    \item $\text{ProfinPNGTinv}_1^{r'}$ the category of exhaustive profinitely filtered pseudo-normed groups with $r'$-action of $T^{-1}$ and strict morphisms.
  \end{itemize}
\end{definition}

\begin{proposition}
  \label{bounded-limits}
  \uses{png-cats}
  \lean{CompHausFiltPseuNormGrp₁.limit_cone_is_limit}
  \leanok
  Consider an inverse system $(X_i)_i$ of compact-Hausdorffly-filtered-pseudonormed abelian groups
  where all transition maps $X_i\to X_j$ send $X_{i,\leq c}$ to $X_{j,\leq c}$.
  Then
  \[ X_{\leq c} := \varprojlim_i X_{i,\leq c} \]
  is compact Hausdorff, and
  \[ X=\bigcup_c X_{\leq c} \]
  is naturally a compact-Hausdorffly-filtered pseudonormed abelian group
  which is the limit of $(X_i)_i$ in the strict category structure.
\end{proposition}

\begin{proof}
  \leanok
  One can define negation and addition on $X$ as continuous maps
  $-: X_{\leq c}\to X_{\leq c}$ and $+: X_{\leq c}\times X_{\leq c'}\to X_{\leq c+c'}$, and these pass to the unions.
  It should then be straightforward to check the axioms.
\end{proof}

% vim: ts=2 et sw=2 sts=2
